Will Kamala Harris will win the 2024 Presidential election

### 2024-11-04 paper/paper.qmd
.

Lastly, if we consider @fig-supportWP we see that harris has been polling at a consistent 48% since mid september which is somewhat similar to Georgia, while Pennsylvania seems to be leaning more democratic than republican than Georgia.@fig-supportGNN, they have both similarly increased their interest in Harris since the polling began until mid september which is when they both becan to plateau at their current polling numbers.

>>>>

Lastly, if we consider @fig-supportWP we see that harris has been polling at a consistent 48% since mid september which is somewhat similar to Georgia, while Pennsylvania seems to be leaning more democratic than republican than Georgia.@fig-supportGNN, they have both similarly increased their interest in Harris since the polling began until mid September which is when they both becan to plateau at their current polling numbers.
